# Brian Palmer

```{r}
library(Biostrings)
library(stringr)
library(dada2)
library(msa)
load(file.path("results/dada2_overlaps.RData"))
amplicon_info <- read.csv("vX_amplicon_info/v4_amplicon_info.tsv", sep = "\t")
```

```{r, include = FALSE}

amplicon_info$amplicon
names(mergers)

mergers[[495]]$sequence <- paste0(dadaFs[[495]]$sequence, "NNNNNNNNNN",
    Biostrings::reverseComplement(
        Biostrings::DNAString(dadaRs[[495]]$sequence)) %>%
            as.character())

mergers[[495]]
```


## Just keep the forward reads

This was proprosed by the author for someone who had 600 bp amplicons with 200 bp reads. https://github.com/benjjneb/dada2/issues/790. 
The downside is this obviously causes loss of information.

```r
seqtab <- gsub("N{10}[ACGT]+", "", getSequences(seqtab))
```

## Possibly could use amplicons from replicates or other samples to determine similarity

```{r}
v <- vector(length = length(mergers))
for (idx in seq_along(mergers)) {
    v[idx] <- nchar(mergers[[idx]]$sequence) > 0 &&
        isTRUE(str_detect(mergers[[idx]]$sequence, "NNNNNNNNNN"))
}

merged_non_overlapping <- mergers[v]
if (length(merged_non_overlapping) > 0) {

    non_overlapping_amplicon <- sub(
        "_PARAV3.*", "", names(merged_non_overlapping))

    v <- str_detect(names(mergers[v]), non_overlapping_amplicon)

    # must have at least 3 reads
    if (sum(v) >= 0)
        msa(mergers[[1]]$sequence, type = "dna", method = "Muscle")
}

```


## A more painful approach reverting to forward and reverse reads.

I'm least confident in this answer.

```{r}
vr <- as.vector(rep(Inf, length(mergers)), mode = "numeric")
vf <- as.vector(rep(Inf, length(mergers)), mode = "numeric")

alignment <- function(fn, x, y) {
    return(fn(x, y))
}
non_overlapping <- mergers[[name]]$sequence

for (i in seq_along(mergers)) {
    name <- names(mergers[i])
    merger_sequence <- mergers[[name]]$sequence
    if (nchar(merger_sequence) > 0 &&
        isTRUE(str_detect(merger_sequence, "NNNNNNNNNN"))) {
            split_merged <- unlist(str_split(merger_sequence, "NNNNNNNNNN"))
            vf[i] <- alignment(adist, split_merged[1], dadaFs[[name]]$sequence)
            vr[i] <- alignment(adist, split_merged[2],
                Biostrings::reverseComplement(
                    Biostrings::DNAString(dadaRs[[name]]$sequence)) %>%
                        as.character())
    }
}

```

